

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "600px")

source("utility/functions.R")

#load data
tweeter <- "alexstubb"
filepath <- paste0("data/",tweeter,"_tweets.Rda")

# raw tweet data
tw <- get(load(filepath))

# tweet data with topics (separated by language)
TW <- get(load(paste0("data/",tweeter,"_topicdata.Rda")))
tweeter_languages <- names(TW)

tw_fi <- TW[["finnish"]]
topic_labels <- c("Kannanottoja", "SuomiNousuun","KookoomusTsemppi","Kansanviestit")

```

# Wellcome

description of the project here

## Explorative analysis

Some basic exploration of the data via pics. Timelines of tweets.

### Scope

```{r, include = FALSE}
mindate <- format(min(tw$created),"%d.%m.%Y")
maxdate <- format(max(tw$created),"%d.%m.%Y")
ntweets <- nrow(tw)
```

mindate     | maxdate     | tweets
----------- | ----------- | -------
`r mindate` | `r maxdate` | `r ntweets`


### Monthly tweets

```{r monthly_tweets}
par(mar=c(8,9,6,4))
h <- hist(tw$created, main = paste(tweeter, "tweets by month"),
     breaks="month", freq=T, 
     xlab="",ylab="", las=2,
     labels=T, cex.axis=1.3, cex.lab=1.5,
     ylim= c(0,400), format="%Y-%m",
     col="cadetblue3")
mtext(side = 2, text = "tweets", line = 5, cex = 1.5)
```

### Daily tweets

```{r daily_tweets}
par(mar=c(7,9,5,3))
h <- hist(tw$created, main = paste(tweeter, "tweets by day"),
          breaks="days", freq=T, 
          xlab="", ylab="",col="grey55", lty=0,
          cex.axis=1.3 ,cex.lab=1.5, tck=0.05, xaxt="n")
peaks=2
tickpos <- h$breaks[order(h$counts,decreasing=T)[1:peaks]]
labels <- names(sort(table(format(tw$created,"%d.%m.%Y")),decreasing=T))[1:peaks]
axis(1, at=tickpos, labels=labels,cex.axis=1.5)
mtext(side = 2, text = "tweets", line = 5, cex = 1.5)
mtext(side = 1, text = "day", line = 3, cex = 1.5)
```

### Hourly tweets

```{r tweets_hour, out.width = "700px"}
hourly <- table(format(tw$created,"%H"))
hourly_prc <- paste(round(100*hourly/sum(hourly),1),"%")
par(mar=c(8,10,5,3))
bp <- barplot(hourly, main = paste(tweeter, "tweets by hour"),
              space=0.5, ylim=c(0,250),
              ylab="",cex.lab=1, cex.names = 1.2,
              cex.axis=1.2, las=2, col = "deepskyblue3",
              xlab="")
text(bp+0.1, hourly, hourly_prc, pos=3, cex=0.7) 
mtext(side = 2, text = "tweets", line = 5, cex = 1.3)
mtext(side = 1, text = "time", line = 5, cex = 1.3)
```

### Most active tweet days

```{r active_days}
top5tweetdays <- sort(table(format(tw$created,"%Y-%m-%d")),decreasing=T)[1:5]
top5tweetdays
```


### Tweet times during the most active days

```{r top_days}
top5days <- names(top5tweetdays)

topdaydata <- lapply(1:4,function(day) {
  get_datedata(tw, top5days[day])
})

newpar <- par(mfrow=c(2,2))
for(i in 1:4){
  time <- topdaydata[[i]]$created
  hist(time, breaks=100,freq=T,border=NULL,ylab="Tweets",
       tck=0,cex.axis=0.8, cex.lab=0.8, xlab="",
       main=paste0(tweeter," ",top5days[i]),
       cex.main=1, ylim=c(0,8))
}
```

### Hashtag frequencies

```{r hashfreq}
hashcounts <- extract_hashes(tw$text)
hash <- head(hashcounts, 5)
kable(hash)
```

```{r hashfreq_plot}
par(las=2, mar=c(5,14,4,2))
barplot(hash$freq, horiz=T, names.arg=hash$tag,
        cex.names=1.3, cex.axis = 1.5,
        col = "skyblue", border=NA)
```

### Most used words

```{r wordclouds, out.height="900px", out.width = "900px"}
# document term matrices for each language
DTM <- get(load(paste0("data/",tweeter,"_DTM.Rda")))

# word frequencies for each language
FREQ <- lapply(DTM, twitter_wordfreqs)
names(FREQ) <- names(DTM)

# wordclouds
par(mfrow= c(3,1))
temp <- lapply(FREQ, function(lang) {
  suppressWarnings(
    wordcloud(lang$word, lang$freq,
            scale = c(5,1),
            random.order=FALSE, colors=brewer.pal(8, "Dark2")))
})

```

knit(input = "readme.Rmd", output = "README.md")
